%\documentclass[margin,line, centered]{res}
\documentclass[12pt, centered, centered]{res_yy}
\usepackage{mathabx}

\oddsidemargin 0.0in
\evensidemargin 0.0in
\textwidth=6.0in
\itemsep=0in
\parsep=0in


\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
      
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}



% An itemize-style list with lots of space between items
\newenvironment{outerlist}[1][\enskip\textbullet]%
        {\begin{enumerate}[#1]}{\end{enumerate}%
         \vspace{-.6\baselineskip}}

% An environment IDENTICAL to outerlist that has better pre-list spacing
% when used as the first thing in a \section
\newenvironment{lonelist}[1][\enskip\textbullet]%
        {\vspace{-\baselineskip}\begin{list}{#1}{%
        \setlength{\partopsep}{0pt}%
        \setlength{\topsep}{0pt}}}
        {\end{list}\vspace{-.6\baselineskip}}

% An itemize-style list with little space between items
\newenvironment{innerlist}[1][\enskip\textbullet]%
        {\begin{compactenum}[#1]}{\end{compactenum}}

% To add some paragraph space between lines.
% This also tells LaTeX to preferably break a page on one of these gaps
% if there is a needed pagebreak nearby.
\newcommand{\blankline}{\quad\pagebreak[2]}



\newsectionwidth{-0.05in}
%\resumewidth{6in}

\begin{document}

\name{Robert Babak Faryabi \vspace*{.1in}}

\begin{resume}
%%%%% Contact %%%%%%%%%%%
%\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{4.5in}p{3in}}
Laboratory of Genome Integrity			& \hspace{-0.4in}{\it Office:}  (301) 435-6485\\
National Cancer Institute                                 & \hspace{-0.4in}{\it Cell:}    (281) 300-3349 \\            
National Institutes of Health    			& \hspace{-0.4in}{\it E-mail:}  faryabib@mail.nih.gov\\         
Bethesda, MD 20892		& \\   %\hspace{-0.4in}{\it Web:} http://ccr.cancer.gov/labs/lab.asp?labid=920     
\end{tabular}

\vspace{-.1in}
\rule{\linewidth}{0.05mm}
%%%% Education %%%%%%%%%%
\section{\sc  Education}
\vspace{0.2in}
\begin{list1}

\item[] {\bf National Institutes of Health}, Bethesda, MD \hfill 2009--present\\
Postdoctoral Research Fellow\\
Mentor: Dr.  Andre Nussenzweig
\vspace{.1in}

\item[] {\bf Texas A\&M University}, College Station, TX \hfill 2005-2009\\
Ph.D. in Computational Biology\\
Adviser: Dr. Edward R. Dougherty
\vspace{.1in}

\item[] {\bf Sharif University of Technology}, Tehran, Iran \hfill 1996-1997\\
M.Sc. in Electrical Engineering
\vspace{.1in}

\item[] {\bf Sharif University of Technology}, Tehran, Iran \hfill 1991-1995\\
B.Sc. in Electrical Engineering 
\end{list1}

\vspace{-.1in}
\rule{\linewidth}{0.05mm}


%%%%%%%%%%%%%%% Journal Publications %%%%%%%%%%%%
\section{\sc Journal Publications}
\vspace{.1in}
*co-first authors
\vspace{.1in}
\begin{enumerate}

\item  M.A. Santos, {\bf {R.B. Faryabi}}, A.V. Ergen, A.M. Day, A. Malhowski, A. Canela, M. Onozawa, J. Lee, E. Callen, P. Gutierrez-Martinez, H. Chen, N. Wong, N. Finkel, A. Deshpande, S. Sharrow, D.J. Rossi, K. Ito, K. Ge, P.D. Aplan, S.A. Armstrong, A. Nussenzweig, ``DNA-Damage Induced Differentiation of Leukemic Cells as an Anti-Cancer Barrier'', \underline{{\emph{Nature}}},  DOI $10.1038$/nature$13483$. 

%\item  F. Polato, E. Callen, N. Wong, {\bf {R.B. Faryabi}}, S. Bunting, H.T. Chen, M. Kozak, M.J. Kruhlak, C.R. Reczek, W.H. Lee, T. Ludwig, R. Baer, L. Feigenbaum, S. Jackson, A. Nussenzweig, ``CtIP-mediated resection is essential for viability and can operate independently of BRCA1'', \newline \underline{{\emph{Journal of Experimental Medicine}}},  211(6):1027-36, Jun 2, 2014

\item  J. Barlow$^{*}$, {\bf {R.B. Faryabi}}$^{*}$, E. Callen, N. Wong, A. Malhowski, H.T. Chen, G. Gutierez-Cruz, H. Sun, P. McKinnon, G. Wright, R. Casellas, D.~F. Robbiani, L. Staudt, O. Fernandez-Capetillo, A. Nussenzweig, ``Identification of Early Replicating Fragile Sites that Contribute to Genome Instability'', \underline{{\emph{Cell}}},  vol.~152, no.~3, pp. 620-632, January 2013.  \underline{*co-first authors}

\item  E. Callen, {\bf {R.B. Faryabi}}, M. Luckey,  B. Hao,  J. Daneil, W. Yang, H.W. Sun, G. Dressler, W. Peng, H. Chi, K. Ge, M. S. Krangel, J. Park, , A. Nussenzweig, ``The DNA Damage- and Transcription-Associated Protein Paxip1 Controls Thymocyte Development and Emigration'',  \underline{{\emph{Immunity}}}, vol.~37, no.~6, pp. 971-985, December 2012.

\item  E. Callen, M. Di Virgilio, M.J. Kruhlak , M. Nieto-Soler, N. Wong, H.T. Chen,  {\bf {R.B. Faryabi}}, F. Polato, M. Santos, L.M. Starnes, D.R. Wesemann, J.E. Lee, A. Tubbs, B.P. Sleckman, J.A. Daniel, K. Ge, F.W. Alt, O. Fernandez-Capetillo, M.C. Nussenzweig, A. Nussenzweig, ``53BP1 Mediates Productive and Mutagenic DNA Repair through Distinct Phosphoprotein Interactions'', \underline{{\emph{Cell}}},  vol.~153, no.~6, pp. 1266-1280, June 2013.

\item  S. Bunting, E. Callen, M. Kozak,  J. Kim,  N. Wong, A. Lopez-Contreras, T. Ludwig, R. Baer, {\bf {R.B. Faryabi}}, A. Malhowski, H.-T Chen, O. Fernandez-Capetillo, A D'Andrea, A. Nussenzweig, ``BRCA1 Functions Independently of Homologous Recombination in DNA Interstrand Crosslink Repair'',  \\ \underline{{\emph{Molecular Cell}}}, vol.~46, no.~2, 27, pp. 125-135, April 2012.

\item G. Vahedi, {\bf {R.B. Faryabi}}, J.-F. Chamberland, A. Datta, E. R. Dougherty, 
``Sampling-Rate-Dependent Probabilistic Boolean Networks'',  \underline{{\emph{Journal of Theoretical Biology}}}, vol.~261, no.~4, pp. 463-477, December 2009.

\item {\bf {R.B. Faryabi}} G. Vahedi, A. Datta, J.-F. Chamberland, E. R. Dougherty, 
``Recent Advances in the Control of Markovian Gene Regulatory Networks'', \underline{{\emph{Current Genomics}}}, vol.~10, no.~7, pp. 540-547, November 2009.

\item G. Vahedi, {\bf {R.B. Faryabi}}, J.-F. Chamberland, A. Datta, E. R. Dougherty, 
``Optimal Intervention Strategies for Cyclic Therapeutic Methods'', \underline{{\emph{IEEE Transactions on Biomedical Engineering}}},  vol.~56, no.~2, pp.~281--291, 
February 2009.

\item {\bf {R.B. Faryabi}}, G. Vahedi, J.-F. Chamberland, A. Datta, E. R. Dougherty, 
``Intervention in Context-Sensitive Probabilistic Boolean Networks Revisited'', \underline{{\emph{EURASIP Journal on Bioinformatics and Systems}}} \underline{{\emph{Biology}}}, vol.~2009, Article ID 360864, 2009.

\item {\bf {R.B. Faryabi}}, J.-F. Chamberland, G. Vahedi, A. Datta, E. R. Dougherty, 
``Optimal Intervention in Asynchronous Genetic Regulatory Networks'', \underline{{\emph{IEEE Journal of Selected Topics in Signal Processing}}}, 
vol.~2, no.~3, pp.~412--423, June 2008.

\item {\bf {R.B. Faryabi}}, G. Vahedi, J.-F. Chamberland, A. Datta, E. R. Dougherty, 
`` Optimal Constrained Stationary Intervention in Gene Regulatory Networks'', \underline{{\emph{EURASIP Journal on Bioinformatics and Systems}}} \underline{{\emph{Biology}}} vol.~2008, Article ID 620767, 2008.

\item G. Vahedi, {\bf {R.B. Faryabi}}, J.-F. Chamberland, A. Datta, E. R. Dougherty, 
``Intervention in Gene Regulatory Networks via a Stationary Mean-First-Passage-Time Control Policy'', \underline{{\emph{IEEE Transactions on}}} \underline{{\emph{Biomedical Engineering}}}, vol.~2, no.~10, 2319-2331, October 2008.

\item {\bf {R.B. Faryabi}}, A. Datta, E. R. Dougherty, 
``On Approximate Stochastic Control in Genetic Regulatory Networks'', \underline{{\emph{IET Journal of Systems Biology}}}, 
vol.~1, no.~6, pp.~361--368, November 2007.

\end{enumerate}

\vspace{-.1in}
\rule{\linewidth}{0.05mm}


%%%%%%%%%%%%%%% Conference Publications %%%%%%%%%%%%
\section{\sc Conference Proceedings}
\begin{enumerate}

\item {\bf {R.B. Faryabi}}, G. Vahedi, J.-F. Chamberland, A. Datta, E. R. Dougherty, 
``Open-Loop Feedback Intervention: Control of Gene Regulatory Networks with Unknown Context'',  in \emph{Workshop on Genomic Signal Processing and Statistics}, 
, Minneapolis, Minnesota, May 2009.

\item {\bf {R.B. Faryabi}}, G. Vahedi, J.-F. Chamberland, A. Datta, E. R. Dougherty, 
``Constrained Intervention in a Cancerous Mammalian Cell-Cycle Network'',  
in \emph{Workshop on Genomic Signal Processing and Statistics}, 
Phoenix, Arizona, June 2008.

\item G. Vahedi, {\bf {R.B. Faryabi}}, J.-F. Chamberland, A. Datta, E. R. Dougherty, 
``Modeling Cyclic Therapy in Gene Regulatory Networks'',  
in \emph{Workshop on Genomic Signal Processing and Statistics}, 
Phoenix, Arizona, June 2008.

\item G. Vahedi, {\bf {R.B. Faryabi}}, J.-F. Chamberland, A. Datta, E. R. Dougherty, 
``Mean First-Passage Time Control Policy versus Reinforcement-Learning Control Policy in Gene Regulatory Networks'',  in \emph{American Control Conference}, 
Seattle, Washington, June 2008.

\item {\bf {R.B. Faryabi}}, J.-F. Chamberland, G. Vahedi, A. Datta, E. R. Dougherty, 
``Optimal Intervention in Semi-Markov-based Asynchronous Genetic Regulatory Networks'',  
in \emph{American Control Conference}, Seattle, Washington, June 2008.

\item {\bf {R.B. Faryabi}}, A. Datta, E. R. Dougherty, 
``On Reinforcement Learning in Genetic Regulatory Networks'',  
in \emph{IEEE Workshop on Statistical Signal Processing}, 
Madison, Wisconsin, August 2007.
\end{enumerate}

\vspace{-.1in}
\rule{\linewidth}{0.05mm}

%%%%%%%%%%%%%%% Invited Presentations %%%%%%%%%%%%
\section{\sc Invited Presentations}
\vspace{.2in}
\begin{list2}
\item[$\diamond$] IEEE Workshop on Genomic Signal Processing and Statistics, Houston, TX, November 2013
%\vspace{0.05in}
\item[$\diamond$] Bioinformatics and Bio-imaging Seminar, Virginia Tech University, Arlington, VA, November 2013
%\vspace{0.05in}
\item[$\diamond$] Center of Excellence in Chromosome Biology Workshop on Chromosome Biology, Bethesda, MD, June 2013
%\vspace{0.05in}
\item[$\diamond$] Green Center for Systems Biology, University of Texas Southwestern Medical Center, Dallas, TX, April 2009
%\vspace{0.05in}
\item[$\diamond$] National Center for Biotechnology Information, Bethesda, MD, March 2009
%\vspace{0.05in}
\item[$\diamond$] ABCS Workshop on Bioinformatics, Computational Biology and Systems Biology, College Station, TX, February 2008
%\vspace{0.05in}
\item[$\diamond$] Institute of Systems Biology, Seattle, WA, June 2008
\end{list2}
\vspace{-.1in}
\rule{\linewidth}{0.05mm}

%%%%%%%%%%%%%%% Honors and Awards %%%%%%%%%%%%
\section{\sc Honors and Awards} 
\vspace{.2in}
\begin{list1}
\item[$\diamond$] Texas A\&M Student Research Award Prize, 2007
%\vspace{0.075in}
\item[$\diamond$] Edward S. Rogers Sr. Scholarship, University of Toronto, ON, Canada, 2004
%\vspace{0.075in}
\item[$\diamond$] Edward S. Rogers Sr. Scholarship, University of Toronto, ON, Canada, 2003
\end{list1}
\vspace{-.1in}
\rule{\linewidth}{0.05mm}

%%%%%%%%%%%%%%% Teaching and Mentoring %%%%%%%%%%%%
\section{\sc Teaching and Mentoring} 
\vspace{.2in}
\begin{list2}
\item[$\diamond$] National Institutes of Health Undergraduate Mentoring: two students, 2013-2014
%\vspace{0.075in}
\item[$\diamond$] Teaching Assistant, Network Programming, University of Toronto, 2005
%\vspace{0.075in}
\item[$\diamond$] Teaching Assistant, System Design \& Technical Communication, University of Toronto, 2004
%\vspace{0.075in}
\item[$\diamond$] Teaching Assistant, Computer Networks, University of Toronto, 2003
\end{list2}
\vspace{-.1in}
\rule{\linewidth}{0.05mm}



%%%%%%%%%%%%%%% Poster Presentations %%%%%%%%%%%%
\section{\sc Conference Presentations}
\vspace{.2in}
\begin{list2}
\item[$\diamond$] Keystone Symposia, DNA Replication and Recombination, Banff, AL, Canada, March 2013
%\vspace{0.05in}
\item[$\diamond$] RECOMB Conference on Regulatory and Systems Genomics, San Francisco, CA, November 2012
%\vspace{0.05in}
\item[$\diamond$] Keystone Symposia, Epigenomics and Chromatin Dynamics, Keystone, CO, January 2012
\end{list2}
\vspace{-.1in}
\rule{\linewidth}{0.05mm}

%%%%%%%%%%%%%%% Media Coverage %%%%%%%%%%%%
\section{\sc Media Coverage} 
\vspace{.2in}
\begin{list2}
\item[$\diamond$] ``Breaking News on Fragile Sites in Cancer'', Cancer Cell, 2013
\item[$\diamond$] ``Damage Control for a Natural Killer'', Cell, 2013
\item[$\diamond$] ``Early Replication Fragile Sites: Where Replication--Transcription Collisions Cause Genetic Instability'', The EMBO Journal, 2013
%\item[$\diamond$] Discovery of new class of damage-prone DNA regions could lead to better cancer treatments, ScienceDaily, 2014
%\vspace{0.075in}
%\item[$\diamond$] Early replication fragile sites: where replication - transcription collisions cause genetic instability, The EMBO Journal, 2013
%\vspace{0.075in}
%\item[$\diamond$] A new mechanism that contributes to the evolution of cancer, ScienceDaily, 2013
%\vspace{0.075in}
\item[$\diamond$] ``DNA Breaks Early in Replication Process Associated with B Cell Cancers'', National Cancer Institute News Note, 2013
%\vspace{0.075in}
%\item[$\diamond$] Discovery of new class of damage-prone DNA regions could lead to better cancer treatments, EurekAlert, 2013
\end{list2}
\vspace{-.1in}
\rule{\linewidth}{0.05mm}

%%%%%%%%%%%%%%% Research Experience %%%%%%%%%%%%
\section{\sc Work \& Research Experience}
\vspace{0.2in}
\begin{list2}
\item[] Postdoctoral Fellow \hfill 2009-present \\
National Cancer Institute, Bethesda, MD
\vspace{0.1in}
\item[] Research Assistant \hfill 2005-2009 \\
Genomic Signal Processing Laboratory, Texas A\&M University, TX
\vspace{0.1in}
\item[] Research Assistant \hfill 2003-2005\\
Wireless and Internet Research Laboratory, University of Toronto, ON, Canada
\vspace{0.1in}
\item[] Design Engineer \hfill 1999-2003\\
Dow Chemical Design \& Construction, Houston, TX
\end{list2}
\vspace{-.1in}
\rule{\linewidth}{0.05mm}


%%%%%%%%%%%%%%% Professional Services %%%%%%%%%%%%
\section{\sc Professional Services} 
\vspace{.2in}
\begin{list2}
\item Technical Program Committee:
%\vspace{0.05in}
\begin{list1}
\item[] IEEE Workshop on Genomic Signal Processing and Statistics, 2014
\item[] IEEE Workshop on Genomic Signal Processing and Statistics, 2013
\end{list1}
%\vspace{0.1in}
\item Reviewer:
%\vspace{0.05in}
\begin{list1}
\item[] IEEE Transactions in Biomedical Engineering, EURASIP Journal of Bioinformatics and Systems Biology, IET Journal of Systems Biology, IEEE Journal of Selected Topics in Signal Processing
\end{list1}
\end{list2}

%%%%%%%%%%%%%%% Professional Affiliation %%%%%%%%%%%%
%\section{\sc Professional Affiliation} 
%\begin{list2}
%\item Member, International Society for Computational Biology (\textbf{ISCB})
%\item Member, Institute of Electrical and Electronics Engineers (\textbf{IEEE})
%\end{list2}


\newpage
\vspace{.03in}
\rule{\linewidth}{0.1mm}
%%%%%%%%%%%%%%% References %%%%%%%%%%%%
\section{\sc References} 
\begin{list1}
%%%%%%%% Ref 1%%%%%%%%%%%%%%%%%%%% 
\item[] \textbf{Dr. Andre Nussenzweig}       
\begin{list2} 		
\item[]  Chief of Laboratory of Genome Integrity
\item[] National Cancer Institute
\item[] Building 37, Room 1108, Bethesda, MD
\item[] (301)-435-6425
\item[] nussenza@mail.nih.gov
\end{list2}
\vspace{.1in}
%%%%%%%% Ref 3%%%%%%%%%%%%%%%%%%%% 
\item[] \textbf{Dr. Edward R. Dougherty}       
\begin{list2} 		
\item[] Director of Center for Bioinformatics and Genomic Systems Engineering
\item[] Texas A\&M University
\item[] Zachry Engineering Center, College Station, TX 77843, USA
\item[] (979) 862-8896
\item[] edward@ece.tamu.edu
\end{list2}
\vspace{.1in}
%%%%%%%% Ref 3%%%%%%%%%%%%%%%%%%%%
\item[] \textbf{Dr Oscar Fernandez-Capetillo}       
\begin{list2} 		
\item[] Leader of Genome Instability Group
\item[] Spanish National Cancer Research Centre
\item[] Melchor Fernandez Almagro, 3\item[] Madrid, 28029, SPAIN
\item[] +34(917)328-000 Ext: 3480
\item[] ofernandez@cnio.es
\end{list2}
\vspace{.1in}
%%%%%%%% Ref 4%%%%%%%%%%%%%%%%%%%%
\item[] \textbf{Dr. Michael Bittner}       
\begin{list2} 		
\item[] Co-Director of Computational Biology Division
\item[] Translational Genomics Research Institute
\item[] 445 N. Fifth Street, Phoenix, AZ 85004, USA 
\item[] (602) 343-8808
\item[] mbittner@tgen.org
\end{list2}
\vspace{.1in}
%
%%%%%%%%% Ref 2%%%%%%%%%%%%%%%%%%%%
%\item[] \textbf{Dr. Aniruddha Datta}       
%\begin{list2} 		
%\item[] Professor of Electrical \& Computer Engineering
%\item[] Texas A\&M University
%\item[] Zachry Engineering Center, College Station, TX 77843, USA
%\item[] (979) 845-5917
%\item[] datta@ece.tamu.edu
%\end{list2}
%\vspace{.1in}
%%%%%%%% Ref 5%%%%%%%%%%%%%%%%%%%%
%\item[] \textbf{Dr. Ilya Shmulevich}       
%\begin{list2} 		
%\item[] Associate Professor
%\item[] Institute for Systems Biology
%\item[] 1441 N 34th Street, Seattle, WA 98103-8904, USA 
%\item[] (206) 732-1212
%\item[] is@ieee.org
%\end{list2}
%\vspace{.1in}
\end{list1}

\end{resume}
\end{document}